The Efficient Handling of Guards \\in the Design of RPython's Tracing JIT

### 2012-09-07 talk/vmil2012/paper.tex
these are done
fix reference

\usepackage{ifthen}
\usepackage{sparklines}
\usepackage{booktabs}
\usepackage{fancyvrb}
\usepackage{color}
\usepackage{colortbl}
\usepackage{wrapfig}
\usepackage{ulem}
\usepackage{xspace}
\usepackage{relsize}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage[pdfpagelabels=true]{hyperref}
\usepackage[colorinlistoftodos]{todonotes}

@@

Tracing just-in-time (JIT) compilers record and compile commonly executed
linear control flow paths consisting of operations executed by an
interpreter.\footnote{There are also virtual machines that have a tracing JIT
compiler and do not use an interpreter~\cite{xxx}. This paper assumes that the
baseline is provided by an interpreter. Similar design constraints would apply
to a purely compiler-based system.}
At points of possible divergence from the traced path operations called guards
are inserted. Furthermore, type guards are inserted to specialize the trace
based on the types observed during tracing. In this paper we describe and
analyze how guards work and explain the concepts used in the intermediate and
low-level representation of the JIT instructions and how these are implemented.
This is done in the context of the RPython language and the PyPy project, which
provides a tracing JIT compiler geared at dynamic language optimization.

@@

\bigtodo{reviewer c: Figure 7 was printed out of order.}

\subsection{Frequency of Guards}
\label{sub:guard_frequency}
\begin{figure*}
    \include{figures/benchmarks_table}
    \caption{Number of operations in the recorded traces and the relative amount of guards before and after optimizations}
    \label{fig:benchmarks}
\end{figure*}

>>>>

\usepackage{ifthen}
\usepackage{sparklines}
\usepackage{booktabs}
\usepackage{fancyvrb}
\usepackage{color}
\usepackage{colortbl}
\usepackage{wrapfig}
\usepackage{ulem}
\usepackage{xspace}
\usepackage{relsize}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage[pdfpagelabels=true]{hyperref}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{flafter}

@@

Tracing just-in-time (JIT) compilers record and compile commonly executed
linear control flow paths consisting of operations executed by an
interpreter.\footnote{There are also virtual machines that have a tracing JIT
compiler and do not use an interpreter~\cite{bebenita_trace-based_2010}. This paper assumes that the
baseline is provided by an interpreter. Similar design constraints would apply
to a purely compiler-based system.}
At points of possible divergence from the traced path operations called guards
are inserted. Furthermore, type guards are inserted to specialize the trace
based on the types observed during tracing. In this paper we describe and
analyze how guards work and explain the concepts used in the intermediate and
low-level representation of the JIT instructions and how these are implemented.
This is done in the context of the RPython language and the PyPy project, which
provides a tracing JIT compiler geared at dynamic language optimization.

@@

\subsection{Frequency of Guards}
\label{sub:guard_frequency}
\begin{figure*}
    \include{figures/benchmarks_table}
    \caption{Number of operations and guards in the recorded traces before and after optimizations}
    \label{fig:benchmarks}
\end{figure*}
